An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex

	\par
	(3) \textit{Algorithms insensitive to AS.}  
%	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
	\textcolor{orange}{Figure~\ref{fig:exp_5_2_3} shows algorithms that are insensitive to AS.}
	Milvus is mainly limited by system-level communication overhead, such as API latency. As a result, its query performance remains largely unaffected by AS variations. ACORN-\(\gamma\) maintains stable performance across different AS settings by using a higher index construction parameter $\gamma$. This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.

>>>>

	\par
	(3) \textit{Algorithms insensitive to AS.}  
	This group includes Milvus and ACORN-\(\gamma\), as illustrated in Figure~\ref{fig:exp_5_2_3}.
	\textcolor{orange}{Figure 1 shows algorithms that are insensitive to AS.}
	Milvus is mainly limited by system-level communication overhead, such as API latency. As a result, its query performance remains largely unaffected by AS variations. ACORN-\(\gamma\) maintains stable performance across different AS settings by using a higher index construction parameter $\gamma$. This ensures a relatively stable average node degree, even after attribute pruning, minimizing the impact of AS changes on query efficiency.
